Time invariant analysis of epidemics with \pkg{EpiCompare}

### 2020-12-16 jss/EpiCompare-paper/EpiCompare-paper.Rmd
small update to final part of paper

```{r echo = FALSE}
devtools::load_all()
library(tidyr)
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)
set.seed(2)

@@

```
However, both models are not a good fit to the filamental path as opposed to the individual points in $(S, I, R)$-space.  What we mean by that is that both models predict epidemic paths that generally have a single defined peak of infection whereas the data certainly looks like it has two distinct peaks, likely caused by our assumed super-spreader event.  In conclusion, \pkg{EpiCompare} makes it clear that, at a glance, 1) the EpiModel network model is a better fit than the Simple SIR model, and 2) the fit is only good at the individual point level as opposed to the epidemic path level.

@@

hagelloch_sir2 <- hagelloch_sir %>%
  rename(t = "time") %>%
  mutate(Type = "true observation",
         sim = 0) %>%
  select(Type, sim, t, S, I, R)
```
```{r}
# after cleaning up and combining 
all_together_df <- rbind(simple_sir,
                         hagelloch_sir2)
all_together_df[c(1:2, nrow(all_together_df) - c(1:0)),]

compression_df <- all_together_df %>% group_by(Type, sim) %>% 
  filament_compression(data_columns = c("S","I","R"), 
                       number_points = 20)
```

>>>>

```{r echo = FALSE}
devtools::load_all()
library(tidyr)
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)
set.seed(1)

@@

However, both models are not a good fit to the filamental path as opposed to the individual points in $(S, I, R)$-space.  This can be captures with the set of simulations both models predict, which all generally have a single defined peak of infection whereas the data certainly looks like it has two distinct peaks, likely caused by our assumed super-spreader event.  This observation is backed up by the below analysis that demonstrates that the estimated psuedo-density of the observed epidemic (relative to the simulations from either model) is much less likely then **any** of the simulations (reported in Table \ref{tab:hags-extreme}. In conclusion, \pkg{EpiCompare} makes it clear that, at a glance, 1) the EpiModel network model is a better fit than the Simple SIR model, and 2) the fit is only good at the individual point level as opposed to the epidemic path level.

@@

hagelloch_sir2 <- hagelloch_sir %>%
  rename(t = "time") %>%
  mutate(Type = "true observation",
         sim = 0) %>%
  select(Type, sim, t, S, I, R)
```
```{r}
#-- after cleaning up and combining --
all_together_df <- rbind(simple_sir,
                         hagelloch_sir2)
```

```{r echo = F}
all_together_df[c(1:2, nrow(all_together_df) - c(1:0)),] %>% 
  kable(booktabs = TRUE,
        caption = paste("Top and bottom 2 rows of \\tt{all\\_together\\_df}\\text{,",
                        "combining both simulated epidemics and the true",
                        "epidemic.}"), label = "cif-all-together-df") %>%
  kable_styling(position = "center", 
                latex_options = "hold_position"
                      )
```

```{r}
compression_df <- all_together_df %>% group_by(Type, sim) %>% 
  filament_compression(data_columns = c("S","I","R"), 
                       number_points = 20)
```

### 2020-12-16 jss/EpiCompare-paper/EpiCompare-paper.tex
small update to final part of paper

However, both models are not a good fit to the filamental path as
opposed to the individual points in \((S, I, R)\)-space. What we mean by
that is that both models predict epidemic paths that generally have a
single defined peak of infection whereas the data certainly looks like
it has two distinct peaks, likely caused by our assumed super-spreader
event. In conclusion, \pkg{EpiCompare} makes it clear that, at a glance,
1) the EpiModel network model is a better fit than the Simple SIR model,
and 2) the fit is only good at the individual point level as opposed to
the epidemic path level.

\begin{CodeChunk}
\begin{CodeInput}
R> # after cleaning up and combining 
R> all_together_df <- rbind(simple_sir,
+                          hagelloch_sir2)
R> all_together_df[c(1:2, nrow(all_together_df) - c(1:0)),]
\end{CodeInput}
\begin{CodeOutput}
# A tibble: 4 x 6
# Groups:   sim [2]
  Type               sim     t     S     I     R
  <chr>            <dbl> <dbl> <dbl> <dbl> <dbl>
1 Simple SIR           1     0   188     0     0
2 Simple SIR           1     1   187     1     0
3 true observation     0    54     1     0   187
4 true observation     0    55     1     0   187
\end{CodeOutput}
\begin{CodeInput}
R> compression_df <- all_together_df %>% group_by(Type, sim) %>% 
+   filament_compression(data_columns = c("S","I","R"), 
+                        number_points = 20)
\end{CodeInput}
\end{CodeChunk}

>>>>

However, both models are not a good fit to the filamental path as
opposed to the individual points in \((S, I, R)\)-space. This can be
captures with the set of simulations both models predict, which all
generally have a single defined peak of infection whereas the data
certainly looks like it has two distinct peaks, likely caused by our
assumed super-spreader event. This observation is backed up by the below
analysis that demonstrates that the estimated psuedo-density of the
observed epidemic (relative to the simulations from either model) is
much less likely then \textbf{any} of the simulations (reported in Table
\ref{tab:hags-extreme}. In conclusion, \pkg{EpiCompare} makes it clear
that, at a glance, 1) the EpiModel network model is a better fit than
the Simple SIR model, and 2) the fit is only good at the individual
point level as opposed to the epidemic path level.

\begin{CodeChunk}
\begin{CodeInput}
R> #-- after cleaning up and combining --
R> all_together_df <- rbind(simple_sir,
+                          hagelloch_sir2)
\end{CodeInput}
\end{CodeChunk}

\caption{\label{tab:cif-all-together-df}Top and bottom 2 rows of \tt{all\_together\_df}\text{, combining both simulated epidemics and the true epidemic.}}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
Type & sim & t & S & I & R\\
\midrule
Simple SIR & 1 & 0 & 188 & 0 & 0\\
Simple SIR & 1 & 1 & 187 & 1 & 0\\
true observation & 0 & 54 & 1 & 0 & 187\\
true observation & 0 & 55 & 1 & 0 & 187\\
\bottomrule
\end{tabular}
\end{table}

\begin{CodeChunk}
\begin{CodeInput}
R> compression_df <- all_together_df %>% group_by(Type, sim) %>% 
+   filament_compression(data_columns = c("S","I","R"), 
+                        number_points = 20)
\end{CodeInput}
\end{CodeChunk}
